Case for Support

### 2021-11-15 detailsOfResource.tex
Started to fill the spike sorting section

@@

\noindent\textcolor{red}{TODO}

>>>>

We propose to add functionality into Bonsai for the implementation of
brain-computer-interface applications illustrated in Figure~\ref{fig:bci}. In
this implementation voltage recordings from the brain will be converted into
spikes fired by single neurons by a \texttt{SpikeSorter}
(Section~\ref{sec:spikeSorting}), or to local field potentials (LFP) by an
\texttt{LFPextractor} (Section~\ref{sec:lfpCalculation}). Next, neural activity
(spikes or LFPs) will be represented in a low-dimensional latent space by a
\texttt{LatentsExtractor}. Finally, a \texttt{Decoder} will extract the
intended behavior of the animal from this low-dimensional representation.

@@

Spike sorting is an essential computational step needed to isolate the activity
of individual neurons, or units, within extracellular recordings which combine
noisy signals from many neurons. Most spike sorting algorithms are designed to
work offline (i.e., identify individual neurons from a complete recording
session, after this session has been completed). We propose to integrate into Bonsai

\paragraph{LFP calculation}
\label{sec:lfpCalculation}

Spikes are extracted from a higher-frequency range of extracellularly recorded
voltages. Local field potentials (LFPs) 
are another important signal to understand brain function, which is extracted
from a lower-frequency range of these voltages. We propose to use in-house
functions implemented in Python to compute LFPs.
